\documentclass[a4paper,twocolumn]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{color}
\usepackage{dirtytalk}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage[style=authoryear]{biblatex}
\addbibresource{main.bib}
\AtEveryBibitem{\clearfield{month}}
\AtEveryBibitem{\clearfield{day}}

\newcommand{\N}{\mathbf{N}}
\newcommand{\Z}{\mathbf{Z}}
\newcommand{\Q}{\mathbf{Q}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\C}{\mathbf{C}}

\author{Florian Fontan}
\title{Advanced Models and Methods in Operations Research \\ Project: Crew pairing}
\date{2023--2024}

\begin{document}

\maketitle

For each problem considered, instances and a code skeleton containing an instance parser and a solution checker are provided in the \texttt{data/} and \texttt{python/} folders of the project.

The algorithms must be implemented in the provided files between the tags \texttt{TODO START} and \texttt{TODO END}.

They must be tested on all the provided instances with the command:
\texttt{python3 problem.py -i instance.json -c certificate.json}

And each solution file must be validated by the provided checker:
\texttt{python3 problem.py -a checker -i instance.json -c certificate.json}

The results must be reproducible.

\bigskip

The delivrable must contain:
\begin{itemize}
  \item A \emph{short} report describing and justifying the proposed algorithms
  \item The code implementing the algorithms
  \item The solution files obtained on the provided instances
\end{itemize}

\section*{Introduction}

Excerpts from~\cite{saddoune_aircrew_2013}.

\begin{quotation}
  A crew pairing is a sequence of flights, connections and rests that starts and ends at a crew base and is assigned to a single crew. The crew pairing problem consists of determining a minimum cost set of feasible crew pairings such that each flight is covered exactly once and side constraints are satisfied.
\end{quotation}

\section{Dynamic Programming}

We consider the following crew pairing problem:
\begin{itemize}
  \item Input:
    \begin{itemize}
      \item $n$ flights; for each flight $j = 1, \dots, n$
        \begin{itemize}
          \item a profit $p_j$
          \item a cost $c^s_j$ of going from the base of the crew to this flight
          \item a cost $c^e_j$ of going from this flight to the base
        \end{itemize}
      \item For each pair of flights $j_1, j_2 = 1, \dots, n$, $j_1 \neq j_2$, a cost $c_{j_1, j_2}$ of going from the arrival of the first one to the departure of the second one. This might not be possible for all pairs of flights.
      \item A maximum number of flights in the pairing $f^\text{max}$
    \end{itemize}
  \item Problem: find a crew pairing, \textit{i.e.}\ a list of consecutive flights such that
    \begin{itemize}
      \item The crew pairing starts and ends at the base
      \item The crew pairing contains at most $f^\text{max}$ flights
    \end{itemize}
  \item Objective: maximize the profit of the crew pairing
\end{itemize}

Propose and implement an algorithm based on Dynamic Programming for this problem.

\section{Heuristic Tree Search}

We consider the following crew pairing problem:
\begin{itemize}
  \item Input:
    \begin{itemize}
      \item $n$ flights; for each flight $j = 1, \dots, n$
        \begin{itemize}
          \item a profit $p_j$
          \item a cost $c^s_j$ of going from the base of the crew to this flight
          \item a cost $c^e_j$ of going from this flight to the base
          \item a duration $t^s_j$ of going from the base of the crew to this flight
          \item a duration $t^e_j$ of going from this flight to the base
          \item a starting time $s_j$
          \item an arrival time $e_j$
        \end{itemize}
      \item For each pair of flights $j_1, j_2 = 1, \dots, n$, $j_1 \neq j_2$
        \begin{itemize}
          \item a cost $c_{j_1, j_2}$ of going from the arrival of the first one to the departure of the second one. This might not be possible for all pairs of flights.
          \item a duration $t_{j_1, j_2}$ of going from the arrival of the first one to the departure of the second one. This might not be possible for all pairs of flights.
        \end{itemize}
      \item A maximum number of flights in the pairing $f^\text{max}$
      \item A maximum duration of a pairing $t^{t, \text{max}}$
      \item A maximum flying time in the pairing $t^\text{max}$
    \end{itemize}
  \item Problem: find a crew pairing, \textit{i.e.}\ a list of consecutive flights such that
    \begin{itemize}
      \item The crew pairing starts and ends at the base
      \item The crew pairing contains at most $f^\text{max}$ flights
      \item The maximum flying time is lesser than $t^{f, \text{max}}$
      \item The duration of the pairing is lesser than $t^{\text{max}}$
    \end{itemize}
  \item Objective: maximize the profit of the crew pairing
\end{itemize}

Propose and implement an algorithm based on Heuristic Tree Search with Dynamic Programming for this problem.

\section{Column Generation \texorpdfstring{\\}{}  + Dynamic Programming}

Propose an exponential formulation and implement an algorithm based on a Column Generation heuristic for this problem.

\section{Column Generation \texorpdfstring{\\}{} + Heuristic Tree Search}

Propose an exponential formulation and implement an algorithm based on a Column Generation heuristic for this problem.

\printbibliography%

\end{document}
